---
title: "HW5 notebook"
output: html_notebook
---

Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, OpenStreetMap, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

```{r}
#Installs the required packages
install.packages(c("tmap", "tmaptools", "rgdal", "sp", "OpenStreetMap", "osmdata"))
```
```{r}
#Load the packages to use them 
library(tmap)
library(tmaptools)
library(rgdal)
library(sp)
library(OpenStreetMap)
library(osmdata)
```

```{r}
#Load the shape file
shpFile <- readOGR("C:/Users/erita/Ekta_Rita_HW5/mygeodata","Locations")
#Read the map using the bounding box of the shape file
osm <- read_osm(bbox(shpFile))
#plot the map layer with the locations layer on top of it and set the size and color of the dots
tm_shape(osm) + tm_raster() + tm_shape(shpFile) + tm_dots(size = 2, col = "red")
```

And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2

```{r}
#Install the required packages
install.packages(c("PBSmapping", "ggmap"))
```
```{r}
#Load the packages to use them
library(PBSmapping)
library(ggmap)
library(maptools)
```
```{r}
#Import the shape file
shapeFile <- importShapefile("C:\\Users\\erita\\Ekta_Rita_HW5\\mygeodata\\Locations")
#Convert it into a  dataframe
locations_df <- as.data.frame(shapeFile)
#get the map with -118.2819356,34.02171339 as the center and zoom it to get a better view
map <- get_map(location = c(-118.2819356,34.02171339), zoom = 15, source = "google")
#Plot the map layer with the data points layer on it. Set the size and color of the points
ggmap(map)+geom_point(data = locations_df, aes(X,Y), size =  3, color = "red")
```


